---
title: "Assignment3.qmd"
format:
  html:
    toc: true
    toc-title: Contents
    toc-location: left
    html-math-method: mathjax
    number-sections: true
editor: visual
author: Himadri Mandal, BS2327
---

# Estimating the estimators

```{r}
mu1 = 10
mu2 = 20
pair <- function(mu){
    v = rnorm(101, mu, 1)
    Mn = mean(v)
    Md = median(v)
    returnV = c(Mn, Md)
}

means1 = c()
medians1 = c()
means2 = c()
medians2 = c()

for(i in 1:10000){
    X = pair(mu1)
    Y = pair(mu2)
    means1 = append(means1, X[1])
    medians1 = append(medians1, X[2])
    means2 = append(means2, Y[1])
    medians2 = append(medians2, Y[2])
    
}
print(c("Standard error of Means:"))
print(c(sd(means1), sd(means2)))
print(c("Standard error of Medians:"))
print(c(sd(medians1), sd(medians2)))
```

Clearly, the standard error of the mean estimator is *significantly* lower than the standard error of the median estimator. Therefore, we conclude that the mean estimator is a better approximation of the unknown $\mu$.

# Is the tangent normal?

```{r}
set.seed(6940)
Theta = runif(1000,0, 2*pi)
X = 1/cos(Theta)
  

hist(X, n = 1000, prob = T, xlim = c(-50,50))

library(MASS)
fit = fitdistr(X, 'normal')
x = seq(-50, 50, 0.01)
curve(dnorm(x, fit$estimate['mean'], fit$estimate['sd']), col = 'blue', add = T, lwd = 2)

```

We cannot represent the points ($a$, $\sqrt{1-a^2}$) and then choose $a$ randomly. Because this will result in a non-uniform distribution (on the circumference). We pick the $\theta$ randomly, instead. Performing the computations we find that

$X=1/{\cos{\theta}}$

This doesn't look normal at all!

# Simulating the smallest window

```{r}
set.seed(6940)
Theta = runif(1000,0, 2*pi)
X = 1/cos(Theta)
  

hist(X, n = 1000, prob = T, xlim = c(-50,50))
L = unname(quantile(X, 0.05))
U = unname(quantile(X, 0.95))

print(U - L)

sum(X>5)/length(X)
```

I assume the distribution is symmetric around $0$ (which it, ideally, is). Then I found $U.L$ by finding the $5^{\text{th}}$ and $95^\text{th}$ quantiles. Clearly then $\{f(X) | X \in [U, L]\}$ has $90\%$ of the values.

$$
U - L = 12.93879
$$

Sir, does this make you happy? I would love to know your opinion.

And the probability of $X>5$ is:

$$
P(X > 5) = 0.059
$$
